A fast unified model for parsing and sentence understanding

### 2016-03-16 writing/hard_stack_paper/batching_fig.tex
Initial revision of abstract and Section 1.
Initial revision of Sections 3, 4, and Bib.
Writing up CP's comments.

\begin{subfigure}[t]{\columnwidth}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

@@

\end{tikzpicture}

@@

\vspace{2em}

\begin{subfigure}[t]{\columnwidth}
\begin{center}
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt}}

@@

    \begin{scope}[shift={(0.9in,-0.8in)}]

@@

\end{tikzpicture}
\end{center}

@@

\caption{An illustration of two standard designs for sentence encoders. Note that the TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence, making batched computation impractical.}
\end{figure}

>>>>

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.75}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black] 
    \tikzstyle{alt}=[fill=orange!40]
    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

@@

\end{tikzpicture}}
\end{center}

@@

\begin{subfigure}[t]{\columnwidth}
\begin{center}
\scalebox{0.75}{
 \begin{tikzpicture}
    \tikzstyle{word}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]    
    \tikzstyle{nonleaf}=[fill=yellow!40,text height=2mm,line width=1pt,draw=black]
    \tikzstyle{alt}=[fill=orange!40]    
    \pgfsetarrowsend{latex}
    \tikzset{edge from parent/.append style={<-, line width=1pt}}

@@

    \begin{scope}[shift={(1.5in,0in)}]

@@

\end{tikzpicture}}
\end{center}

@@

\caption{An illustration of two standard designs for sentence encoders. The TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence, making batched computation impractical.}
\end{figure}
